---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

# HW4 Part 2 MGT 6203 

## Instructions:


**For Homework 4 Part 2, please use this R notebook in Vocareum to submit your solutions. Vocareum is an educational cloud platform for programming in several languages; it is based on the Jupyter notebook environment. This platform allows us to move homework assignments to the cloud. The advantages are that all of you will be working in the same coding environment AND peer reviewers will be able to run your R code easily. This way we eliminate some issues we might encounter when working on an individual/local basis, such as library installations and Rstudio OS requirements; R notebooks work on mobile platforms and tablets.**

**With R notebooks, you will be learning a new way of presenting data analysis reports, that is neat and flexible, where formatted (English) text and (R) code can easily coexist on the same page. Notebooks can be also collaborative when needed. For now, we are asking each of you to do your own work for homework. Think of R notebooks as interactive program-based Google docs or MS-Office 360 docs; these are gradually replacing local files on our computers. **

**Many of you are new to the R notebooks and Vocareum platforms. We will provide TA help in Piazza with specific code if you have questions. Here we list some important things to get you started. Please read through them carefully.**


<ol>
<li>Even though we are moving from your local envrionment to the cloud, **our expectations from your homework will remain the same**. Same goes for the rubrics.</li>

<li>Vocareum has its own cloud based file system, the data files you will be using for the assignments will be stored in the cloud with path **"../resource/asnlib/publicdata/FILENAME.csv"**. You will be able to import them with the same method as you do in RStudio, simply substitute the path name to the one specified in the instructions. You won't be able to modify these data files.</li>

<li>You will be able to find the data files on Canvas/EdX if you would like to explore them offline.</li>

<li>**For coding questions, you will be graded on the R code as well as the output** in your submission.</li>

<li>**For interpretations or short response questions, please type the answers in the notebook's markdown cells**. To change a code cell to a markdown cell, click on the cell, and in the dropdown menu above, switch the type of the cell block from "code" to "markdown". **Adding print statements to code cells for short response/interpretation questions is also fine, as long as we can clearly see the output of your response**.</li>

<li>You don't need to, but if you would like to learn more about how to format your markdown cells, visit the following site: https://www.earthdatascience.org/courses/intro-to-earth-data-science/file-formats/use-text-files/format-text-with-markdown-jupyter-notebook/. Jupyter notebook also support LaTeX.</li>

<li>**Feel free to delete or add as many additional cells as you need**. But please try to keep your notebook clean and keep your solution to a question directly under that question to avoid confusions.</li>

<li>You may delete the #SOLUTION BEGINS/ENDS HERE comments from the cell blocks, they are just pointers that indicates where to put you solutions.</li>

<li>**When you have finished the assignment, remember to rerun your notebook to check if it runs correctly.** You can do so by going to **Kernel-> Restart & Run All**. You may lose points if your solutions does not run successfully.</li>

<li>**Click the "Submit" button on the top right corner to turn in your assignment**. Your assignment will enter the next phase for peer review.</li>

<li>**You are allowed a total of 2 submissions for this assignment.** So make sure that you submit your responses carefully. You will be able to come back and resubmit your assignment as long as it is before the start of the peer review period.</li>

<li>**Please remember to finish the peer reviews after you have submitted your assignment.** You are responsible for grading the work of three of your peers thoroughly, and in addherence to the rubrics. And you will be held accountable for peer grading. **There will be a 30% penalty to your grade if you fail to complete one or more peer reviews in proper fashion.**</li>

<li>Feel free to address your questions, concerns, and provide any feedback on Piazza. We will continuously try to improve going forward.</li>

<li>Good Luck!</li>

</ol>

# About Package Installation:

Most of the packages (if not all) that you will need to complete this assignment are already installed in this environment. An easy way to check this is to run the command: library(PackageName). If this command runs successfully then the package was already installed and has been successfully attached to the code. If the command gave an error saying the Package was not found then follow the steps below to successfully install the package and attach it to the code: 

Use *installed.packages()* command to return a table of the packages that are preinstalled in the environment.

To attach a preinstalled library in Vocareum, simply use *library(PackageName)*

**To install a package that does not come with the provided environment, please use the following syntax:**

*install.packages("PackageName", lib="../work/")*

**To attach a library you just installed, use the following syntax:**

*library(PackageName, lib.loc="../work/")*

Make sure the file location is the same as the above code snippets *("../work/")*

## Question 1

### A) You have started your position as transportation director in a small town called Mountainside Village. There is only one road in and out of town. Today you can expect at peak traffic to see 20 cars per hour and the drive along the road with no traffic is 1 minute. Assuming Poisson arrival and exponential drive times, what is the current utilization of the road? (3 points) 

```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```

### B) How long will a person spend on the road? (3 points) 


```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```

### C) With the arrival of a new company traffic is expected to increase to 45 cars per hour. What happens to the utilization and how long does an average driver spend on the road now? (3 points) 

```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```
### D) Graph how wait times have increased with each additional car. (3 points) 

```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```

### E) The cost to build a new road is expensive, so the mayor wants to ensure that there is at least a 25% probability that there are 3 or more cars waiting in traffic before they approve funding for a new road. Prove to the mayor that the budget is justified. (3 points) 
```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```
### F) Graph the decreasing probability per car before and after the factory. 

**Hint:** The independent variable x will be the number of cars waiting and y will be the probability that x –number of cars or less are waiting. (5 points) 

```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```

## Question 2

### ABC Lab is a cement manufactory lab and they are working on a new process to make cement. They make multiple cement samples and test the strength of them. In the dataset, you will find the strength of 8 randomly selected samples (MPa) from the production line everyday for 59 days.  They want to use statistical control chart to test if the process is in control. 

 

*Note:* Please use the following to load the dataset:  

data <-read.csv("../resource/asnlib/publicdata/concrete.csv", stringsAsFactors = FALSE) 

### A) Calculate ULCx, LCLx, ULCr, LCLr (8 points) 

```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```


### B) Plot X-Bar and R-Bar, make sure to include UCL and LCL in the charts. Observe the two charts, comment if you see any points beyond control limits, or any trends and patterns.  Do you think there is any assignable cause of variation? (8 points) 

```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```

### C) If the required specification of the strength of the cement is between 25 and 45 MPa, calculate process capability ratio (Cp), and process capability index (Cpk).  According to Cp and Cpk, is the process capable of meeting the required specifications? (4 points)

```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```

## Question 3

**Some important information of the data is:** 

**Source:** http://archive.ics.uci.edu/ml/datasets/Individual+household+electric+power+consumption 

**Data Set Information:** 

This archive contains 2075259 measurements gathered in a house located in Sceaux (7km of Paris, France) between December 2006 and November 2010 (47 months). 

**Notes:** 
1.(global_active_power*1000/60 - sub_metering_1 - sub_metering_2 - sub_metering_3) represents the active energy consumed every minute (in watt hour) in the household by electrical equipment not measured in sub-meterings 1, 2 and 3. 
2.The dataset contains some missing values in the measurements (nearly 1,25% of the rows). All calendar timestamps are present in the dataset but for some timestamps, the measurement values are missing: a missing value is represented by the absence of value between two consecutive semi-colon attribute separators. For instance, the dataset shows missing values on April 28, 2007. 


**Attribute Information:** 

1.date: Date in format dd/mm/yyyy 
2.time: time in format hh:mm:ss 
3.global_active_power: household global minute-averaged active power (in kilowatt) 
4.global_reactive_power: household global minute-averaged reactive power (in kilowatt) 
5.voltage: minute-averaged voltage (in volt) 
6.global_intensity: household global minute-averaged current intensity (in ampere) 
7.sub_metering_1: energy sub-metering No. 1 (in watt-hour of active energy). It corresponds to the kitchen, containing mainly a dishwasher, an oven and a microwave (hot plates are not electric but gas powered). 
8.sub_metering_2: energy sub-metering No. 2 (in watt-hour of active energy). It corresponds to the laundry room, containing a washing-machine, a tumble-drier, a refrigerator and a light. 
9.sub_metering_3: energy sub-metering No. 3 (in watt-hour of active energy). It corresponds to an electric water-heater and an air-conditioner. 

** Lets first load the dataset :** 

```{r}
#library(dplyr)

#data <-read.csv("../resource/asnlib/publicdata/household_power_consumption.csv", stringsAsFactors = FALSE) 
#data <- data[rowSums(is.na(data)) == 0,]

#data$Global_active_power <- as.numeric(data$Global_active_power)
#data$Sub_metering_1 <- as.numeric(data$Sub_metering_1)
#data$Sub_metering_2 <- as.numeric(data$Sub_metering_2)
#data$Sub_metering_3 <- as.numeric(data$Sub_metering_3)
#data1 <- data %>% mutate(power_per_minute = Global_active_power*1000/60 - Sub_metering_1 - Sub_metering_2 - Sub_metering_3)

#head(data1)
```

### A) What is the average value of daily data consumed in watt hours? (4 points) 

**Note:** There are NA values present, so while finding the mean, use the attribute na.rm=TRUE or alternatively na.omit 

```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```

### B)  Using an alpha of 0.35 and h = 100, use the ses() function from the ‘forecast’ package to fit the data, and plot the model. What do you observe in the graph? (4 points) 

**Note:** You will need to convert the dataframe to an xts object. 

**Note:** In case of NA values, fill them using the function na.locf(df) from the xts package. 

```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```

### C) For three values of alpha value of (0.05, 0.35, 0.75) and h of 100, calculate and report the tracking signal. (8 points)

```{r}
# SOLUTION BEGINS HERE


# SOLUTION ENDS HERE
```

### D) What does the tracking signal (sign and value) for each of the alpha values suggest about the models? Are any of the models not a good fit for the data? (4 points)

```{r}
## Answer to 'What does the tracking signal (sign and value) for each of the alpha values suggest about the models?'
## Alpha of 0.05
# The value of the tracking signal suggests that: 
# The sign of the tracking signal suggests that: 

## Alpha of 0.35
# The value of the tracking signal suggests that: 
# The sign of the tracking signal suggests that: 

## Alpha of 0.75
# The value of the tracking signal suggests that: 
# The sign of the tracking signal suggests that: 

## Answer to 'Are any of the models not a good fit for the data?'
#
```

